Compiling refinement types to dependent types

### 2020-07-02 tex/paper.tex
Fix spaces
Use coloneqq
Describe terms translation

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}

@@

For the example oracle being an SMT solver and the syntax of terms also including mathematics, $[|\ |]$ might be defined as
\begin{equation}
\begin{aligned}
  & [| \emptyset |] = \top																						\\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] = [| \nonterm G |] \land [| \{x/v\} \nonterm r |]   \\
  & [| \nonterm r_1 \land \nonterm r_2 |] = [| \nonterm r_1 |] \land [| \nonterm r_2 |]							\\
  & \cdots TODO
\end{aligned}
\end{equation}

@@

@@

\begin{itemize}
  \item Non-dependent function type:
	\[
	  \tau_1 \rightarrow \tau_2 := \Pi x : \tau_1. \tau_2,
	\]
	where $\tau_2$ does not have $x$ free.
  \item Dependent pair type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
	\[
	  \{ x : \tau\ **\ P x \} := \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha.
	\]
  \item Accessing the first and second component of the dependent pair:
	\[
	  \text{fst} := TODO,
	\]
	\[
	  \text{snd} := TODO.
	\]
  \item Non-dependent pair type:
	\[
	  (\tau_1, \tau_2) := \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
	\]
\end{itemize}

@@

>>>>

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}

@@

For the example oracle being an SMT solver and the syntax of terms also including mathematics, $[|\ |]$ might be defined as
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \coloneqq \top																						 \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \coloneqq [| \nonterm G |] \land [| \{x/v\} \nonterm r |] \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \coloneqq [| \nonterm r_1 |] \land [| \nonterm r_2 |]		 \\
  & \cdots TODO
\end{aligned}
\end{equation}

%TODO define substitutions on the \nonterm r

@@

We take $\lambda C$ \cite{Nederpelt14} enriched with integers and case-splitting as our core dependently typed language.

@@

\begin{itemize}
  \item Non-dependent function type:
  \[
    \tau_1 \rightarrow \tau_2 \coloneqq \Pi x : \tau_1. \tau_2,
  \]
  where $\tau_2$ does not have $x$ free.
  \item Dependent pair type, or $\Sigma$-type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
  \[
    \{ x : \tau\ **\ P x \} \coloneqq \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha.
  \]
  \item Accessing the first and second component of the dependent pair:
  \[
    \text{fst} \coloneqq TODO,
  \]
  \[
    \text{snd} \coloneqq TODO.
  \]
  \item Non-dependent pair type:
  \[
    (\tau_1, \tau_2) \coloneqq \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
  \]
\end{itemize}

@@

We translate the surface language types and terms using the $\mu_\tau$ and $\mu_\varepsilon$ functions respectively.
$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{tS}_1) \rightarrow \nonterm{tS}_2)  && \coloneqq \Pi x : \mu_\tau(\nonterm{tS}_1). \mu_\tau(\nonterm{tS}_2)  \\
  & \mu_\tau( \{ v : \nonterm{tS} | \nonterm{r} \})             && \coloneqq \{ v : \mu_\tau(\nonterm{tS})\ **\ \mu_\tau(\nonterm r) \}  \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \coloneqq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))          \\
  & \mu_\tau( \nonterm{eS} )                                    && \coloneqq \mu_\varepsilon(\nonterm{eS}) = \text{True}                 \\
  & \mu_\tau(B)                                                 && \coloneqq B                                                           \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements (which are $\text{Bool}$-typed terms) are translated to propositions stating that the corresponding term is equal to $\text{True}$,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}
